\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-07-07 latex_secondsubmission_reviewcomments/ReviewCommentsResponse.tex

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}
\definecolor{SolutionColor}{rgb}{0.1,0.3,1}
\usepackage{lipsum}

\renewcommand{\thequestion}{\alph{question} }
\renewcommand\questionlabel{\llap{\thequestion)}}

%\pointsinrightmargin
%\boxedpoints
\unframedsolutions
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.9,0.9,1}
\renewcommand{\solutiontitle}{}

\usepackage{titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

% \setlength{\droptitle}{-10em}   % This is your set screw

\title{Review Comment Responses to Journal of Building Performance Simulation Second Submission}
\subtitle{Paper Title: Urban and building multiscale co-simulation: case study implementations on two university campuses 
}
% \email{clayton@nus.edu.sg}
% \author{Clayton Miller, Daren Thomas, J\'er\^ome K\"ampf, Arno Schlueter}

% \subtitle{ETH Z\"urich, Institute of Technology in Architecture (ITA), Architecture and Sustainable Building Technologies (SuAT)}
% \subtitle{*Corresponding author: Phone: +1-402-403-0090, miller.clayton@arch.ethz.ch}

\begin{document}

\maketitle

\section{Review Comments}
\begin{questions}

\question p. 13, line 69. “we week to co-simulate” is incorrect. Please consider “we co-simulate.”
\begin{solution}
Fixed -- thanks for catching that!
\end{solution}

\question  p. 12, lines 90-93. The correction the authors made in response to a reviewer comment
needs further modification. My comment was “Please note that Bueno et al. 2013 generated urban weather with a nodal model and did not directly couple EnergyPlus to a nodal representation of the urban canopy layer. The accuracy of this approach depends on how faithfully users and the model represent the buildings that will later be simulated in detail in EnergyPlus with the modified weather file.” This applies to Bueno et al. 2013 and NOT Bueno et al. 2011, in which TEB and EnergyPlus are coupled. In short, one of Bueno’s papers employed coupling and the other did not; the authors should distinguish them or refer to the single method of their choice.
\begin{solution}
Very good point - apologies for misunderstanding that point. The Bueno 2013 paper has been removed as it does not utilize coupling.
\end{solution}

\question p. 14, line 149. Please delete the redundant “per hour” after “timesteps.”
\begin{solution}
Fixed.
\end{solution}

\question P. 15, lines 176-177. In two places, the “l” in “long-wave” should be capitalized. 
\begin{solution}
Good catch - good example of why "find and replace" needs to be performed before final proofreading.
\end{solution}

\question P. 16, line 189. Please hyphenate “urban scale.”
\begin{solution}
This instance has been hyphenated as well as several others in the manuscript
\end{solution}

\question p. 17, line 217. Please replace “simulation results of the co-simulation” with “results of
the co-simulation.”
\begin{solution}
Fixed.
\end{solution}

\question p. 18, line 221. Please replace “actualized” with “actual.” In line 224, please replace
“measured and simulated” with “measurement and simulation.”
\begin{solution}
Fixed.
\end{solution}

\question p. 20, line 283. Please replace “co- simulation” with “co-simulation” by removing the
extraneous space after the hyphen.
\begin{solution}
Fixed.
\end{solution}

\question p. 21, Figures 10 and 11. The authors have usefully improved these figures. Is it
necessary to retain the absolute change in energy consumption, to four significant figures, as well as the percentage change? This reviewer suggests that the absolute change be removed because it suggests more precision that the process merits and because the percentages are more meaningful.
\begin{solution}
We agree with this and have changed to figures to only represent the percentage change.
\end{solution}

\question p. 21, section 3.5. The new reference to the Minergie standard should be placed after “Minergie building” or at the end of that sentence, and not at the end of the paragraph.
\begin{solution}
Fixed.
\end{solution}

\question p. 19, line 260. Online sources use “plug load” rather than plug-load.” Either is better than “plug- load” (with both a hyphen and a space), as used in the text.
\begin{solution}
Fixed.
\end{solution}

\question  p. 24, lines 348-353. The new discussion section includes two redundancies. In the first sentence, please consider deleting “on two real-world case studies,” given the reference to case studies at the beginning of the sentence. The third sentence could be ended with “...unique to this case study....”
\begin{solution}
The first redundancy was fixed. For the second one, we removed "in this particular instance", but kept the "unique to this case study" were it is
\end{solution}

\question  p. 25, lines 368-375. In line 372, please hyphenate “case-study” (when used as a modifier for campuses). In line 373, please remove the space after the hyphen in “co- simulation.”
\begin{solution}
Fixed
\end{solution}

\question   p. 25, lines 376-379. The text identifies “practical implementation of retrofit scenarios” and “retrofit analysis” as future applications. How do these applications differ?
\begin{solution}
We removed the second reference to retrofits and, instead, changed it to refer to general "systems analysis"
\end{solution}

\question   p. 26, line 416. Only the K in KAEMPF should be capitalized.
\begin{solution}
Fixed.
\end{solution}

\end{questions}
\end{document}

### 2017-07-07 latex_thirdsubmission_compared/UMEM_CoSim_original.tex
Made second revision changes

\subsection{Acknowledgments}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

>>>>

% \subsection{Acknowledgments}
% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
% Thoma for their assistance in this project. This research was funded by the
% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
% Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

### 2017-07-07 latex_thirdsubmission_corrected/UMEM_CoSim.tex
Made second revision changes

\author{Clayton Miller\textsuperscript{a,b}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
Daren Thomas\textsuperscript{b},
J\'er\^ome K\"ampf\textsuperscript{c},
and Arno Schlueter\textsuperscript{b}\\
\vspace{6pt}
\textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
\textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
}

@@

\begin{abstract}
The co-simulation of both urban and building-level models leverages the advantages of both platforms. It better accounts for the localized effects of surrounding buildings, geography and climate conditions while maintaining high-fidelity building systems representation. This paper describes the co-simulation process of the building and urban scale models of two university campuses in Switzerland using EnergyPlus and CitySim. In the first case study, on-site measured performance data is compared to the co-simulation results. The second case study examines the results of the two engines. The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on heating use as compared to solo simulations.The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study. It was able to substantially reduce the discrepancies in prediction between the engines in the other study.

    % The co-simulation of both urban and building-level models provides the means to model 
    % collections of buildings in ways that leverage the advantages of both platforms. It accounts better 
    % for the localized effects of surrounding buildings, geography and climate conditions 
    % while maintaining a high-fidelity building systems representation.
    % This paper describes the co-simulation process of the building and urban
    % scale models of two campuses of higher education buildings in Switzerland.
    % The campuses are modeled at both the building level, using the EnergyPlus
    % simulation engine, and at the urban scale using the CitySim engine. A co-
    % simulation framework is used to execute simulations from both engines
    % concurrently with an exchange of information to leverage the various
    % strengths of each. In the first case study, on-site weather and measured
    % performance data are then compared to the output from two modeling
    % scenarios: building-scale simulation using EnergyPlus and co-simulation of
    % the engines.  The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study and was able to 
    % highly reduce the discrepancies in prediction between the engines in the other study.
     % Challenges encountered with the urban scale
    % calibration and the strengths and weaknesses of the developed process are
    % discussed.
    % A partial calibration process is implemented to reconcile the
    % simulations with the measured data of a targeted office building on
    % campus. In the second case study, the co-simulation results are compared
    % to the CitySim simulation engine.

    % A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each.

    % The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
    % -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
    % heating consumption as compared to solo simulations of each of the engines.
\end{abstract}

@@

Urban scale building performance simulation is a process that empowers the
analysis and optimization of cities. Urban populations are growing around the
world at an unprecedented rate. A transition from urban to rural is underway and
2.5 billion people are expected to join cities throughout the world by the year 2050
\citep{united_nations_world_2014}. Expansions of entire districts and even cities
is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
modeling is in the midst of an intense focus on the research community with
six key areas of practice: technology design, building design, urban climate,
systems design, policy assessment, and land use and transportation
\citep{keirstead_review_2012}. The ability to simulate the interaction between
large collections of buildings enables the development and testing of
optimization and planning scenarios for this new development
\citep{dorer_modelling_2013}.

@@

Building performance simulation is a mature domain of research relative to
urban scale efforts. The use of whole building simulation engines originated
in the 1960's with the US government's development of the BLAST and DOE-2
hourly energy simulation programs \citep{lawrie_energyplus:_2001}. In 1996, development
on a new simulation engine, EnergyPlus, began in order to combine the
advantages of previous efforts in a single, modular program. EnergyPlus, as a
result, has become a popular choice in detailed whole-building performance
simulation due to the breadth of mechanical, renewable, and electrical systems
that can be modeled. EnergyPlus specifically excels in its ability to model
unique mechanical system types such as decoupled centralized cooling
\citep{miller_modeling_2010}. Additionally, EnergyPlus is designed to provide a high
resolution in which internal loads and natural ventilation technologies can be
modeled in detail at the building level. EnergyPlus is also extensively used within the
research community and has new features that enable it to couple with other simulation programs.

Both building and urban-scale simulation domains have rightfully chosen
boundary conditions that reflect their key goals while seeking to minimize the
input parameters necessary and run-times of the engines themselves. This focus
results in certain deficiencies concerning modeling various phenomena.
For example, urban scale simulation highly simplifies the building systems and
internal load models, thus making a retrofit analysis at the systems level
difficult. And whole building simulation in EnergyPlus neglects many of the
various contextual consideration of the urban environment such as long-wave
radiation exchange with adjacent surfaces and localized urban weather effects
\citep{lawrie_energyplus:_2001}.

The current
effort seeks to couple building and urban scale simulation to address the deficiencies of the individual engines. The research in
this paper is part of a larger coupling effort in which various engines are
connected and co-simulated to create a more comprehensive analysis of the
urban scale \citep{dorer_modelling_2013,allegrini_influence_2012}. The target is the
computational interface between the building energy model, using EnergyPlus,
and the urban energy model using CitySim. An overview of the larger scope is
shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as 
the interface between the City Energy Simulation (CES) model and the
Building Energy Simulation (BES) model. The scales and models contained in the 
urban environment context include the Urban-Scale Model (UC Model), the Urban 
Microclimate (UMC) model using OpenFoam, and the Meteorological Meso-scale (MM model) 
using Climate Limited-Area Modeling (COSMO-CLM). On the database side, Revit, Global 
Information Systems (GIS), and building information systems (BIS) are utilized.

@@

This paper describes the achievement of several objectives. The first is to
automate the process of simultaneous meta-data extraction from a
Building Information Model (BIM) for the creation of both building and
urban-scale performance models for a real-world campus of buildings. Next, we week to 
co-simulate the urban and building scale models through concurrent information exchange.
Finally, we implement a simplified calibration procedure for the first scenario by 
reconciling the co-simulation output results for a target building using measured energy 
performance data from the campus energy information system (EIS)

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{wetter_co-simulation_2011,trcka_co-simulation_2010}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{zhang_coupled_2013} and to improve energy prediction
\citep{bouyer_microclimatic_2011}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{yang_integrated_2012}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{martin_estimation_2015}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
through a modified weather file to quantify the influences of urban localized weather effects
on whole building simulation \citep{bueno_combining_2011} and urban weather generation
\citep{bueno_urban_2013}.

@@

The number of timesteps per hour for both CitySim and EnergyPlus is set to one per hour. 
The frequency of data exchanges is set to once per timestep. No data averaging over time 
is performed. Data exported from one simulation engine overwrites the corresponding data
in the other simulation engine at each timestep. Each simulation is performed for a whole 
year.

@@

\subsection{long-wave radiation exchange}
\label{lwradiation}
long-wave radiation exchange in the urban scale environment is coupled in the
co-simulation process. It requires the development of a set of
approximations to reduce the number of coupled variables between the engines
and to account for differences in the methods by which each engine calculates
this value. A detailed description of long-wave Radiation (LWR) variable
exchange and approximation is found in a previously published study
\citep{miller_long_2015} on a simplified theoretical case.

@@

\subsection{Simplified calibration}
In the first case study, one aspect of this analysis is the comparison of the actual measured performance of the target building on campus with the
simulation results of the co-simulation. A simplified calibration procedure is
adapted from previous research to compare the measured heating and cooling
data available on campus with various simulation scenarios
\citep{samuelson_analysis_2015}. This calibration procedure was utilized in the
performance reconciliation of 18 buildings that were built according to the
LEED Canada protocol and were under review of actualized performance. This
protocol is unique in its analysis process to uncover design model
deficiencies in a step-wise manner, utilizing the most readily available
knowledge first and working towards equilibrium between measured and
simulated. There is an appropriate balance between the effort of implementation and value
generated through the calibration process.

% The following steps are the general procedure applied to the targeted buildings:

% \begin{enumerate}
%   \item Using the local weather conditions for the simulation period
%   \item Update simulation based on custom lighting schedules and power densities extracted from the measured data
%   \item Update simulation based on custom plug load schedules and power densities extracted from the measured data
%   \item Account for \emph{unregulated} building loads such as experimental equipment and process loads
% \end{enumerate}

@@

\subsection{Measured data collection and calibration}
Energy data from the HPI building was collected and analyzed in the context of
the simplified calibration procedures. The measured datasets were screened and
aggregated into typical usage profiles to be used for the lighting, plug-
loads, and HVAC equipment availability schedules and power densities. Figure
\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
energy for the HPI building. This profile was created through a filtering and
clustering process known as \emph{DayFilter} \citep{miller_automated_2015}. Cluster 0 represents
the typical energy profile for Sunday, while Cluster 1 dominates the Saturdays of the data set.
Clusters 2 and 3 make up most of the weekdays of the data set with Cluster 3 being more common in 
non-summer months. These profiles are used to set the availability schedules as inputs into the
EnergyPlus simulation to emulate the way occupants inhabit the building and
how the building management system (BMS) controls the lighting and HVAC
systems.

@@

\subsection{EnergyPlus co-simulation results}
For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 6.5\% due to co-simulation. The exchange of long-wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.

% These performance differences due to co-simulation are compared to a
% theoretical single-zone case study in which there was a 15-30\% increase in
% heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
% The results from this case study are less extreme on the heating side and more
% on the cooling side than the theoretical case study.

@@

\subsection{Campus case study 2: EPFL Quartier Nord} 
Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de
Lausanne (EPFL) campus located at its northwest corner. This complex includes
a Convention Centre with an auditorium with a maximum capacity of 3000
(seated) people, housing for 516 students, retail and service areas and a
hotel. As a public space, this ensemble is organized around the central plaza as
seen in Figure \ref{fig:quartier_nord_1}). With a particularly strong visual and formal identity, the SwissTech
Convention Centre (STCC) is clearly the key protagonist.  Designed as a
Minergie building, it includes modern energy conversion
technologies to reduce its energy consumption. The focus of the co-simulation
is realized on the STCC, simulated with the nearby buildings for housing,
retail and service areas \citep{beyeler_minergie:_2009}.

@@

% \subsection{CitySim co-simulation results}

% When focusing solely on CitySim, a 26.9\% decrease in heating energy is
% observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
% decrease in heating energy is observed, as seen in Figure
% \ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
% previous comparison of EnergyPlus and CitySim engines. The substantial
% differences between solo and co-simulation in these cases is a result of
% EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
% interpreting these results -- you mentioned that there is an expected delta
% between citysim and energyplus in previous studies. Can you help elaborate on
% that?}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
% \label{fig:qn_citysim_cosimvssolo_cooling}
% \end{figure}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
% \label{fig:qn_citysim_cosimvssolo_heating}
% \end{figure}

\section{Discussion}
Two campus case studies were presented in this paper to showcase a unique process of extracting model meta-data, conversion of those data into input files for two separate simulation engines, and the solo
and co-simulation process of those engines on two real-world case studies. The analysis of the results shows that for the first case study, co-simulation can achieve values closer to measured reality for heating, but not cooling. 
These results are unique to this case study and simply show that the co-simulation process may be helpful for heating only
in this particular instance. A limitation of this study is that we only analyze a single building against measured data in this
context. In the second case study, significant discrepancies are found between the CitySim and EnergyPlus engines which were corrected using the co-simulation process.
% This section will outline 
% the advantages and disadvantages of undertaking this process with respect to factors such as 
% usability for various applications, simulation speed and resources, and an overview of the tools 
% involved in the process.

% Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
% this study.

One of the key insights in this work is that each of the engines is enabled to account for the various 
physical phenomenon in their simulation process that were previously impossible. For example, 
through co-simulation, EnergyPlus was able to utilize the long-wave radiation exchange capabilities 
of CitySim. The ability to couple and leverage the best aspects of multiple simulation
engines can enhance the modeling of large-scale urban agglomerations. 
% This paper has outlined two such scenarios in which the building-focused EnergyPlus
% simulation engine is coupled and co-simulated with the urban-scale CitySim
% engine.

@@

\section{Conclusion}
This paper outlines the implementation of a fully automated workflow
process that extracts geometry information at the
urban-scale, creates the necessary input information, executes each engine
with information exchange at each time step of targeted variables, and
accumulates the results of the analysis. The process has been implemented on
simplified theoretical scenarios in the past, and the key innovation with this
work is in implementation on actual case study campuses and targeted
buildings. The results illustrate that the differences between the co-
simulation and solo environments are within range of previous theoretical
models. More reliable results of the magnitude of differences between the
simulation techniques can be extracted from these real-world scenarios.

Future work in using co-simulation models for buildings and campuses would
more intensively utilize the model results in a practical implementation of
retrofit scenarios or urban-scale energy systems research. More implementations would 
also test the feasibility of using co-simulation for retrofit analysis, urban planning studies, and
cooling and heating system optimization.

\subsection{Acknowledgments}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

>>>>

\author{Clayton Miller\textsuperscript{a,b}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
Daren Thomas\textsuperscript{a},
J\'er\^ome K\"ampf\textsuperscript{c},
and Arno Schlueter\textsuperscript{a}\\
\vspace{6pt}
\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
}

@@

\begin{abstract}
The co-simulation of both urban and building-level models leverages the advantages of both platforms. 
It better accounts for the localized effects of surrounding buildings, geography and climate conditions 
while maintaining high-fidelity building systems representation. This paper describes the co-simulation process 
of the building and urban-scale models of two university campuses in Switzerland using EnergyPlus and CitySim. 
In the first case study, on-site measured performance data is compared to the co-simulation results. 
The second case study examines the results of the two engines. The results show that coupling of EnergyPlus with 
CitySim resulted in a -15.5\% and -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on heating 
use as compared to solo simulations.The co-simulation process was able to better model realistic conditions for 
heating, but not cooling in one case study. It was able to substantially reduce the discrepancies in prediction between the engines in the other study.
\end{abstract}

@@

Urban-scale building performance simulation is a process that empowers the
analysis and optimization of cities. Urban populations are growing around the
world at an unprecedented rate. A transition from urban to rural is underway and
2.5 billion people are expected to join cities throughout the world by the year 2050
\citep{united_nations_world_2014}. Expansions of entire districts and even cities
is not an uncommon phenomenon, especially in East Asia and Africa. Urban-scale
modeling is in the midst of an intense focus on the research community with
six key areas of practice: technology design, building design, urban climate,
systems design, policy assessment, and land use and transportation
\citep{keirstead_review_2012}. The ability to simulate the interaction between
large collections of buildings enables the development and testing of
optimization and planning scenarios for this new development
\citep{dorer_modelling_2013}.

@@

Building performance simulation is a mature domain of research relative to
urban-scale efforts. The use of whole building simulation engines originated
in the 1960's with the US government's development of the BLAST and DOE-2
hourly energy simulation programs \citep{lawrie_energyplus:_2001}. In 1996, development
on a new simulation engine, EnergyPlus, began in order to combine the
advantages of previous efforts in a single, modular program. EnergyPlus, as a
result, has become a popular choice in detailed whole-building performance
simulation due to the breadth of mechanical, renewable, and electrical systems
that can be modeled. EnergyPlus specifically excels in its ability to model
unique mechanical system types such as decoupled centralized cooling
\citep{miller_modeling_2010}. Additionally, EnergyPlus is designed to provide a high
resolution in which internal loads and natural ventilation technologies can be
modeled in detail at the building level. EnergyPlus is also extensively used within the
research community and has new features that enable it to couple with other simulation programs.

Both building and urban-scale simulation domains have rightfully chosen
boundary conditions that reflect their key goals while seeking to minimize the
input parameters necessary and run-times of the engines themselves. This focus
results in certain deficiencies concerning modeling various phenomena.
For example, urban-scale simulation highly simplifies the building systems and
internal load models, thus making a retrofit analysis at the systems level
difficult. And whole building simulation in EnergyPlus neglects many of the
various contextual consideration of the urban environment such as long-wave
radiation exchange with adjacent surfaces and localized urban weather effects
\citep{lawrie_energyplus:_2001}.

The current
effort seeks to couple building and urban-scale simulation to address the deficiencies 
of the individual engines. The research in
this paper is part of a larger coupling effort in which various engines are
connected and co-simulated to create a more comprehensive analysis of the
urban-scale \citep{dorer_modelling_2013,allegrini_influence_2012}. The target is the
computational interface between the building energy model, using EnergyPlus,
and the urban energy model using CitySim. An overview of the larger scope is
shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as 
the interface between the City Energy Simulation (CES) model and the
Building Energy Simulation (BES) model. The scales and models contained in the 
urban environment context include the Urban-Scale Model (UC Model), the Urban 
Microclimate (UMC) model using OpenFoam, and the Meteorological Meso-scale (MM model) 
using Climate Limited-Area Modeling (COSMO-CLM). On the database side, Revit, Global 
Information Systems (GIS), and building information systems (BIS) are utilized.

@@

This paper describes the achievement of several objectives. The first is to
automate the process of simultaneous meta-data extraction from a
Building Information Model (BIM) for the creation of both building and
urban-scale performance models for a real-world campus of buildings. Next, we co-simulate 
the urban and building scale models through concurrent information exchange.
Finally, we implement a simplified calibration procedure for the first scenario by 
reconciling the co-simulation output results for a target building using measured energy 
performance data from the campus energy information system (EIS)

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{wetter_co-simulation_2011,trcka_co-simulation_2010}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{zhang_coupled_2013} and to improve energy prediction
\citep{bouyer_microclimatic_2011}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{yang_integrated_2012}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{martin_estimation_2015}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
through a modified weather file to quantify the influences of urban localized weather effects
on whole building simulation \citep{bueno_combining_2011}.

@@

The number of timesteps for both CitySim and EnergyPlus is set to one per hour. 
The frequency of data exchanges is set to once per timestep. No data averaging over time 
is performed. Data exported from one simulation engine overwrites the corresponding data
in the other simulation engine at each timestep. Each simulation is performed for a whole 
year.

@@

\subsection{Long-wave radiation exchange}
\label{lwradiation}
Long-wave radiation exchange in the urban-scale environment is coupled in the
co-simulation process. It requires the development of a set of
approximations to reduce the number of coupled variables between the engines
and to account for differences in the methods by which each engine calculates
this value. A detailed description of Long-wave Radiation (LWR) variable
exchange and approximation is found in a previously published study
\citep{miller_long_2015} on a simplified theoretical case.

@@

\subsection{Simplified calibration}
In the first case study, one aspect of this analysis is the comparison of the actual 
measured performance of the target building on campus with the 
results of the co-simulation. A simplified calibration procedure is
adapted from previous research to compare the measured heating and cooling
data available on campus with various simulation scenarios
\citep{samuelson_analysis_2015}. This calibration procedure was utilized in the
performance reconciliation of 18 buildings that were built according to the
LEED Canada protocol and were under review of actual performance. This
protocol is unique in its analysis process to uncover design model
deficiencies in a step-wise manner, utilizing the most readily available
knowledge first and working towards equilibrium between measurement and
simulation. There is an appropriate balance between the effort of implementation and value
generated through the calibration process.

@@

\subsection{Measured data collection and calibration}
Energy data from the HPI building was collected and analyzed in the context of
the simplified calibration procedures. The measured datasets were screened and
aggregated into typical usage profiles to be used for the lighting, plug loads, and HVAC equipment availability schedules and power densities. Figure
\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
energy for the HPI building. This profile was created through a filtering and
clustering process known as \emph{DayFilter} \citep{miller_automated_2015}. Cluster 0 represents
the typical energy profile for Sunday, while Cluster 1 dominates the Saturdays of the data set.
Clusters 2 and 3 make up most of the weekdays of the data set with Cluster 3 being more common in 
non-summer months. These profiles are used to set the availability schedules as inputs into the
EnergyPlus simulation to emulate the way occupants inhabit the building and
how the building management system (BMS) controls the lighting and HVAC
systems.

@@

\subsection{EnergyPlus co-simulation results}
For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. 
Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 6.5\% due to co-simulation. The exchange of long-wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.

@@

\subsection{Campus case study 2: EPFL Quartier Nord} 
Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de
Lausanne (EPFL) campus located at its northwest corner. This complex includes
a Convention Centre with an auditorium with a maximum capacity of 3000
(seated) people, housing for 516 students, retail and service areas and a
hotel. As a public space, this ensemble is organized around the central plaza as
seen in Figure \ref{fig:quartier_nord_1}). With a particularly 
strong visual and formal identity, the SwissTech
Convention Centre (STCC) is clearly the key protagonist.  Designed as a
Minergie building, it includes modern energy conversion
technologies to reduce its energy consumption \citep{beyeler_minergie:_2009}. The focus of the co-simulation
is realized on the STCC, simulated with the nearby buildings for housing,
retail and service areas.

@@

\section{Discussion}
Two campus case studies were presented in this paper to showcase a unique process of extracting model meta-data, conversion of those data into input files for two separate simulation engines, and the solo
and co-simulation process of those engines. The analysis of the results shows that for the first case study, co-simulation can achieve values closer to measured reality for heating, but not cooling. 
These results are unique to this case study and simply show that the co-simulation process may be helpful for heating only. A limitation of this study is that we only analyze a single building against measured data in this
context. In the second case study, significant discrepancies are found between the CitySim and EnergyPlus engines which were corrected using the co-simulation process.

One of the key insights in this work is that each of the engines is enabled to account for the various 
physical phenomenon in their simulation process that were previously impossible. For example, 
through co-simulation, EnergyPlus was able to utilize the long-wave radiation exchange capabilities 
of CitySim. The ability to couple and leverage the best aspects of multiple simulation
engines can enhance the modeling of large-scale urban agglomerations.

@@

\section{Conclusion}
This paper outlines the implementation of a fully automated work flow
process that extracts geometry information at the
urban-scale, creates the necessary input information, executes each engine
with information exchange at each time step of targeted variables, and
accumulates the results of the analysis. The process has been implemented on
simplified theoretical scenarios in the past, and the key innovation with this
work is in implementation on actual case-study campuses and targeted
buildings. The results illustrate that the differences between the co-simulation 
and solo environments are within range of previous theoretical
models. More reliable results of the magnitude of differences between the
simulation techniques can be extracted from these real-world scenarios.

Future work in using co-simulation models for buildings and campuses would
more intensively utilize the model results in a practical implementation of
retrofit scenarios or urban-scale energy systems research. More implementations would 
also test the feasibility of using co-simulation for systems analysis, urban planning studies, and
cooling and heating system optimization.

\subsection{Acknowledgments}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project.
